%Overall Info
\newcommand{\ddName}{Laurel}
\newcommand{\ddClass}{Wizard}
\newcommand{\ddLevel}{2}
\newcommand{\ddBackground}{Sage}
\newcommand{\ddPlayerName}{Erik}
\newcommand{\ddRace}{Vedalken}
\newcommand{\ddAlignment}{chaotic-good}
\newcommand{\ddXP}{9000+}

\newcommand{\ddAge}{43}
\newcommand{\ddGender}{female}
\newcommand{\ddHeight}{2,05m}
\newcommand{\ddWeight}{81kg}
\newcommand{\ddEyes}{green}
\newcommand{\ddSkin}{pale}
\newcommand{\ddHair}{dark black}

%stats
\newcommand{\ddInspiration}{0}
\newcommand{\ddArmor}{12}
\newcommand{\ddInitiative}{2}
\newcommand{\ddSpeed}{9,5}
\newcommand{\ddProficiency}{2}

\newcommand{\ddStrength}{11}
\newcommand{\ddDexterity}{14}
\newcommand{\ddConstitution}{15}
\newcommand{\ddIntelligence}{16}
\newcommand{\ddWisdom}{12}
\newcommand{\ddCharisma}{13}
\newcommand{\ddSanity}{11}
\newcommand{\ddPerception}{11}
\newcommand{\ddMaxHP}{12}
\newcommand{\ddCurrentHP}{12}
\newcommand{\ddTemporaryHP}{0}

%Skills; being proficient: 1, else: 0;
    %Saving throws
    \newcommand{\ddsStrength}{0}
    \newcommand{\ddsDexterity}{0}
    \newcommand{\ddsConstitution}{0}
    \newcommand{\ddsIntelligence}{1}
    \newcommand{\ddsWisdom}{1}
    \newcommand{\ddsCharisma}{0}
    %Skills
    \newcommand{\ddsAcrobatics}{0}
    \newcommand{\ddsAnimal}{0}
    \newcommand{\ddsArcana}{1}
    \newcommand{\ddsAthletics}{0}
    \newcommand{\ddsDeception}{0}
    \newcommand{\ddsHistory}{1}
    \newcommand{\ddsInsight}{0}
    \newcommand{\ddsIntimidation}{0}
    \newcommand{\ddsInvestigation}{1}
    \newcommand{\ddsMedicine}{1}
    \newcommand{\ddsNature}{0}
    \newcommand{\ddsPerception}{0}
    \newcommand{\ddsPerformance}{0}
    \newcommand{\ddsPersuasion}{0}
    \newcommand{\ddsReligion}{1}
    \newcommand{\ddsSleight}{0}
    \newcommand{\ddsStealth}{0}
    \newcommand{\ddsSurvival}{0}

%Death?
\newcommand{\ddSuccess}{0}
\newcommand{\ddFail}{0}

%Languages & Features
\newcommand{\ddLanguages}{\small Common Vedalken Elvish Dwarvish}
\newcommand{\ddProficiencies}{\small dagger darts slings Q-staff l.-crossbow}
\newcommand{\ddFeatures}{\small\textbf{Partially Amphibous -\\}You can breathe underwater for up to 1 hour per long rest.\\\textbf{Researcher -\\}When you attempt to learn or recall a piece of lore, if you do not know that information, you often know where and from whom you can obtain it.\\\textbf{Arcane Recovery -\\}Once per day when you finish a short rest, you can choose expended spell slots to recover. The spell slots can have combined level that is equal or less than half your wizard level (rounded up), and none of the slots can be 6th lvl or higher.\\\textbf{Necromancy Savant -\\}The gold and time you must spend to copy a necromancy spell into your spellbook is halved.\\\textbf{Grim Harvest -\\}Once per turn when you kill one or more creatures with a spell you regain hit points equal to twice the spell's lvl, or three times if the spell belongs to the School of Necromancy. You don't gain this benefit for killing constructs or undead.}

%Weapons
\newcommand{\ddWoneName}{Q-staff 1h}
\newcommand{\ddWoneBonus}{2}
\newcommand{\ddWoneDMG}{1d6~BLT}

\newcommand{\ddWtwoName}{Q-staff 2h}
\newcommand{\ddWtwoBonus}{2}
\newcommand{\ddWtwoDMG}{1d8~BLT}


%Personality
\newcommand{\ddTraits}{\small I'm convinced that people are always trying to steal my secrets.}
\newcommand{\ddIdeals}{\small Nothing should fetter the infinite possibility inherent in all existence.}
\newcommand{\ddBonds}{\small It is my duty to protect my students.}
\newcommand{\ddFlaws}{\small I overlook obvious solutions in favor of the complicated ones.}
\newcommand{\ddBackstory}{Until her thirties she was an apprentice of a wizard that is slightly involved in dark magic. She is intrigued by it and always wants to learn more about it. At the age of 41, one year after she reached the age of adults, her sage got fed up and kicked her out. Since the she wanders around on the search for the perfect dark magic: Necromancy.}
